---
title: "Homework #5, Choice #1"
author: "Rachel Kanaziz"
date: "11/11/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, options(tigris_use_cache = TRUE))
library(tidyverse)
library(reshape2)
library(tigris)
library(sf)
library(viridis)
```

# Homicide Data

Read in the data. 

```{r read data}
homicide_raw <- read_csv("../data/homicide-data.csv")
```

## Clean Data

Filter the data for the city of Denver and select the categories that will be used. 

```{r denver}
denver <- homicide_raw %>% 
  filter(city == "Denver") %>% 
  select(lat, lon, disposition, victim_race)
```

## Map Boundaries

In this section, I used the zip codes for the Denver area to create boundaries for my base map. 

```{r zips}
denver_zips <- zctas(cb = TRUE, starts_with = c("802"), class = "sf")
plot(denver_zips)
```

## Number of Homicides by Victim Race

Here, I determined the three race groups (balck, white, hispanic) with the highest number of victim homicides. 

``` {r race}
race <- denver %>% 
  group_by(victim_race) %>% 
  mutate(count=n()) %>% 
  arrange(desc(count)) %>% 
  ungroup()

denver2 <- denver %>%
  filter(victim_race == c("Black", "White", "Hispanic")) %>% 
  mutate(disposition = factor(disposition, levels = c("Closed without arrest", "Closed by arrest", "Open/No arrest"), 
                      labels = c("solved", "solved", "unsolved")))
```


## Create the Map

I created a map to show where the homicides in Denver have occured for the three race groups with the highest number of victims. Then, I faceted by the disposition of the case in order to create two stacked maps. 

```{r, map, fig.width = 10, dpi=300}
denver_crs <- denver2 %>% 
  filter(!is.na(lat)) %>% 
  st_as_sf(coords = c("lon", "lat")) %>% 
  st_set_crs(4269)

map <- ggplot() + 
  geom_sf(data = denver_zips, color = "lightgray") + 
  geom_sf(data = denver_crs, aes(color = factor(victim_race)), show.legend = 'point') +
  ggtitle("Homicides in Denver, CO") +
  scale_color_manual(values = c("Black" = "black", "Hispanic" = "red", "White" = "yellow"),
                     labels = c("Black", "Hispanic", "White"),
                     name = "Victim Race") +
  labs(x = "Longitude", y = "Latitude") +
  facet_wrap(~ disposition, ncol = 1) +
  theme(plot.title = element_text(hjust = 0.5))

map

```
